---
title: "Lab03"
author: "Siddhartha Sinha"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# AIM: Testing of hypothesis for different population mean when sd is known

# DATASET:
```{r}
iris
```
## DATASET DESCRIPTION:
This famous Fisher's or Anderson's iris data set gives the measurements in centimeters of the variables sepal length, sepal width, petal length and petal width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, Iris versicolor, and Iris virginica.

# DIMENSION OF THE DATASET:
```{r}
dim(iris)
```
Here we can see that our dataset has 150 rows and 5 columns.

# FIRST 6 OBSERVATIONS:
```{r}
head(iris)
```
Here we can see the first 6 observations of the iris dataset.

# LAST 6 OBSERVATIONS:
```{r}
tail(iris)
```
Here we can see the last 6 observations of the iris dataset.

# DESCRIPTIVE STATISTICS:

## SUMMARY OF THE DATASET:
```{r}
summary(iris)
```
Here we can see the minimum value, the first quartile, median (second quartile), third quartile , mean and the maximum value of each of the 5 columns of the data set. Let our target variable be "sepal length".

# IMPORTING LIBRARY:
```{r}
library(BSDA)
library(dplyr)
```
Here we install the "dplyr" (data set plier) package for making data manipulation easier the "BSDA" (Basic Statistics and Data Analysis) package.

# POPULATION 1:
```{r}
population1=filter(iris, Species=="virginica")
population1
```
## POPULATION 1 DESCRIPTION:
Here we can see that we have filtered out only the "virginica" species from the iris data set.

## DIMENSION OF POPULATION 1:
```{r}
dim(population1)
```
Here we can see that the filtered out "virginica" species has a total of 50 observations.

# FINDING TARGET VARIABLE OF POPULATION 1:
```{r}
p1 = population1$Sepal.Length
p1
```

## MEAN OF THE POPULATION 1 OF TARGET VARIABLE:
```{r}
mean(p1)
```
Here we have the mean of our population 1 (with "sepal length of virginica species" as target variable) is 6.588.

# SD OF THE POPULATION 1 OF TARGET VARIABLE:
```{r}
sd(p1)
```
Here we have the sd of our population 1 (with "sepal length of virginica species" as target variable) is 0.6358796.

# SAMPLE 1:
```{r}
samplesize1 = 30
s1 = sample(p1, 30, replace = FALSE)
s1
```
Here we can the see the 25 "sepal length" samples chosen by simple random sampling by without replacement technique from the population of 50 "virginica" observations.

# POPULATION 2:
```{r}
population2=filter(iris,Species=="setosa")
population2
```
## POPULATION 2 DESCRIPTION:
Here we can see that we have filtered out only the "setosa" species from the iris dataset.

## DIMENSION OF POPULATION 1:
```{r}
dim(population2)
```
Here we can see that the filtered out "setosa" species has a total of 50 observations.

# FINDING TARGET VARIABLE FROM POPULATION 2:
```{r}
p2 = population2$Sepal.Length
p2
```

## MEAN OF THE POPULATION 2 OF TARGET VARIABLE:
```{r}
mean(p2)
```
Here we have the mean of our population 2 (with "sepal length of setosa species" as target variable) is 5.006.

# SD OF THE POPULATION 2 OF TARGET VARIABLE:
```{r}
sd(p2)
```
Here we have the sd of our population 2 (with "sepal length of virginica species" as target variable) is 0.3524897.

# SAMPLE 2:
```{r}
samplesize2 = 30
s2 = sample(p2, 30, replace = FALSE)
s2
```
Here we can the see the 25 "sepal length" samples chosen by simple random sampling by without replacement technique from the population of 50 "setosa" observations.


# Z TEST



# TWO TAILED:
## TO TEST WHETHER THE TWO MEANS ARE EQUAL OR NOT:
H0: mean1 = mean2
H1: mean1 != mean2
```{r}
z.test (x=s1, y=s2, alternative = "two.sided", mu=0, sigma.x = sd(p1), sigma.y = sd(p2), conf.level = 0.95)
```
Here we tried to do a two tailed Z-test where our null hypothesis is both mean are equal and our alternative hypothesis is both means are not equal. After proceeding with the test, we can see that our p value is less than 0.05, thus, we reject the null hypothesis as there is enough evidence to suggest a significant difference.



# ONE TAILED:
## TO TEST WHETHER MEAN 1 IS LESS THAN MEAN 2 OR NOT:
H0: mean1 = mean2
H1: mean1 < mean2
```{r}
z.test (x=s1, y=s2, alternative = "less", mu=0, sigma.x = sd(p1), sigma.y = sd(p2), conf.level = 0.95)
```
Here we tried to do a one tailed Z-test where our null hypothesis is both means are equal and our alternative hypothesis is mean 1 is less than mean 2. After proceeding with the test, we can see that our p value is greater than 0.05, thus, we accept the null hypothesis as there is not enough evidence to suggest a significant difference.

## TO TEST WHETHER MEAN 1 IS GREATER THAN MEAN 2 OR NOT:
H0: mean1 = mean2
H1: mean1 > mean2
```{r}
z.test (x=s1, y=s2, alternative = "greater", mu=0, sigma.x = sd(p1), sigma.y = sd(p2), conf.level = 0.95)
```
Here we tried to do a one tailed Z-test where our null hypothesis is both mean are equal and our alternative hypothesis is where mean 1 is greater than mean 2. After proceeding with the test, we can see that our p value is less than 0.05, thus, we reject the null hypothesis as there is enough evidence to suggest a significant difference.















