---
title: "Lab04"
author: "Siddhartha Sinha"
date: "`r Sys.Date()`"
output: word_document
---

# AIM: Test for proportion of single population using Prop Test and Binom Test

# INTRODUCTION: 
The data set contains information about students, including their race, family background, lunch status and academic performances. The focus here is on exploring the gender distribution within a subset of this data.
The analysis involves sampling 100 students and assessing the proportion of males within this sample. A hypothesis test is performed to evaluate whether this sample proportion is significantly different from the assumed population proportion.

# DATASET: 
```{r}
library(readxl)
StudentsPerformance <- read_excel("C:/Users/Siddhartha/Downloads/StudentsPerformance.xls")
```
Here we imported the data set 

```{r}
head(StudentsPerformance)
```
Here we obtained the first six rows from our StudentsPerformance data set.

```{r}
tail(StudentsPerformance)
```
Here we obtained the last six rows from our StudentsPerformance data set.

```{r}
dim(StudentsPerformance)
```
Here we can see that our data set contains 1000 rows and 8 columns.

```{r}
summary(StudentsPerformance)
```
Here we can see the minimum value, the first quartile, median (second quartile), third quartile , mean and the maximum value of each of the 8 columns of the data set.

```{r}
library(dplyr)
```
Here we install the "dplyr" (data set plier) package for making data manipulation easier

```{r}
s = sample(1:nrow(StudentsPerformance), 100, replace = FALSE)
new = StudentsPerformance[s,]
count_val = count(new, gender)
count_val
```
Here we get 100 samples using the 

```{r}
class(new)
```


# SETTING THE HYPOTHESIS:

Po: Proportion of Sex Male 
Assume, the population proportion
H0: Po = 0.50 vs H1: Po != 0.50
```{r}
x=41
n=100
prop.test(x, n, p = 0.50, alternative = "two.sided", conf.level = 0.95)
```







